---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE}
library(stringr)

date <- "11/09/2017"
vendor <- "Pizza Capri"
title <- "Title of Talk"
file_title <- "Title of Talk"
short_title_n = 3
speaker <- "Damon Centola"
department <- "Associate Professor in the Annenberg School for Communication, Director of the Network Dynamics Group"
university <- "University of Pennsylvania"
github_home <- "https://github.com/uchicago-computation-workshop"


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")
repo_page <- paste(github_home, repo, sep="/")

#Create File Name Parts
short_title <- small_title(file_title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Computational Social Science Workshop Presents </h3>

<h1 class=pfblock-header3> `r speaker` </h1>
<h3 class=pfblock-header3> `r department` </h3>
<h3 class=pfblock-header3> `r university` </h3>

<br><br>



<p class=pfblock-header3>The <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> at the University of Chicago cordially invites you to attend this week's talk:</p>

<br>

<div class=pfblock-header3>
<h2 class=pfblock-header> 
  <a href="`r paper_link`" >`r title`</a>
</h2>

<br>
</div>

<p class=footertext2> 

</p>

<br>

<h4 class=pfblock-header3> Thursday, `r date` </h4>
<h4 class=pfblock-header3> 11:00am-12:20pm </h4>
<h4 class=pfblock-header3> Kent 120 </h4>

<br>

<p class=pfblock-header3>A light lunch will be provided by `r vendor`.</p>

<br><br>

<!--Insert Faculty Bio Here-->



<p class=footertext2> 

**Damon Centola** is an Associate Professor in the Annenberg School for Communication at the University of Pennsylvania, where he is Director of the <a href="http://ndg.asc.upenn.edu/"> Network Dynamics Group </a>. Before coming to Penn, he was an Assistant Professor at M.I.T. and a Robert Wood Johnson Fellow at Harvard University. Centola completed his Ph.D. in sociology at Cornell University where he was an NSF IGERT Fellow in Non-linear Dynamics and Complex Systems. He is currently a Fellow at the Center for Advanced Study in the Behavioral Sciences at Stanford University. 

Centola’s work addresses the theory of how behaviors spread through social networks. His research uses computational models and online experiments to study innovation diffusion, social epidemiology and cultural evolution. His papers have been published across several disciplines, including sociology, physics, and public health, appearing in journals such as Science, the Proceedings of the National Academies of Sciences, and the American Journal of Sociology. His work received the American Sociological Association’s Award for Outstanding Article in Mathematical Sociology in 2006, 2009, and 2011, and has garnered the ASA's Goodman Award for Outstanding Contributions to Sociological Methodology. He has developed new computational and experimental technologies, including the NetLogo Agent Based Modeling environment, and was awarded a U.S. Patent for inventing a method for building online networks to promote diffusion. Recent popular accounts of Centola’s work have appeared in The New York Times, Wired, and CNN. His research has been funded by the Robert Wood Johnson Foundation, the National Science Foundation, the National Institutes of Health, the James S. McDonnell Foundation, and the Hewlett Foundation. 
</p>




<br><br>

---

<p class=footertext> The 2017-2018 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> meets each Thursday from 11 to 12:20 p.m. in Kent 120. All interested faculty and graduate students are welcome.</p> 

<p class=footertext>Students in the Masters of Computational Social Science program are expected to attend and join the discussion by posting a comment on the <a href="`r issues_page`"> issues page </a> of the <a href="`r repo_page`"> workshop's public repository on GitHub.</a> Further instructions are documented in the Computational Social Science Workshop's <a href="https://github.com/uchicago-computation-workshop/README"> README on Github.</a></p>


